Loop

### 2021-04-05 executableMS/ms_v1.rmd
Update ms_v1.rmd

---
authors:
  - Susanne RK Zajitschek
  - Felix Zajitschek
  - Russell Bonduriansky
  - Robert C Brooks
  - Will Cornwell
  - Daniel S Falster
  - Malgorzata Lagisz
  - Jeremy Mason
  - Alistair M Senior
  - Daniel WA Noble
  - Shinichi Nakagawa
  - Evolution & Ecology Research Center, School of Biological, Earth, and Environmental Sciences, University of New South Wales, Sydney, Australia; 
  - Liverpool John Moores University, School of Biological and Environmental Sciences, Liverpool, United Kingdom; 
  - European Bioinformatics Institute (EMBL- EBI), European Molecular Biology Laboratory, Wellcome Trust Genome Campus, Hinxton, United Kingdom; 
  - University of Sydney, Charles Perkins Centre, School of Life and Environmental Sciences, School of Mathematics and Statistics, Sydney, Australia; 
  - Division of Ecology and Evolution, Research School of Biology, Australian National University, Canberra, Australia

bibilography: SexDiffBib.bib

---

@@

## Introduction
Sex differences arise because selection acts on the two sexes differently, especially on traits associ- ated with mating and reproduction (Darwin, 1871). Therefore, sex differences are widespread, a fact which is unsurprising to any evolutionary biologist. However, scientists in many (bio-)medical fields have not necessarily regarded sex as a biological factor of intrinsic interest (Clayton, 2016; Flanagan, 2014; Karp et al., 2017; Klein et al., 2015; Prendergast et al., 2014; Shansky and Woolley, 2016). Therefore, many (bio-)medical studies have only been conducted with male sub- jects. Consequently, our knowledge is biased. For example, we know far more about drug efficacy in male compared to female subjects, contributing to a poor understanding of how the sexes respond differently to medical interventions (Nowogrodzki, 2017). This gap in knowledge is predicted to lead to overmedication and adverse drug reactions in women (Zucker and Prendergast, 2020). Only recently have (bio-)medical scientists started considering sex differences in their research (Dorris et al., 2015; Ingvorsen et al., 2017; Robinson et al., 2017; Smarr et al., 2017;Ahmad et al., 2017; Foltin and Evans, 2018; Thompson et al., 2018). Indeed, the National Insti- tutes of Health (NIH) have now implemented new guidelines for animal and human research study designs, requiring that sex be included as a biological variable (Clayton, 2016; Clayton and Collins, 2014; NIH, 2015a). [@moore2001]
When comparing the sexes, biologists generally focus on mean differences in trait values, placing little or no emphasis on sex differences in trait variability (see Figure 1 for a diagram explaining differences in means and variances). Despite this, two hypotheses exist that explain why trait variability might be expected to differ between the sexes. Interestingly, these two hypotheses make opposing predictions.

 this stupid figure has to get embedded Fig1 (./executableMS/Figures/Figure 1.png).

@@

Fig2(./executableMS/Figures/Figure 2.png)

>>>>

---
authors:
  - Susanne RK Zajitschek
  - Felix Zajitschek
  - Russell Bonduriansky
  - Robert C Brooks
  - Will Cornwell
  - Daniel S Falster
  - Malgorzata Lagisz
  - Jeremy Mason
  - Alistair M Senior
  - Daniel WA Noble
  - Shinichi Nakagawa
  - Evolution & Ecology Research Center, School of Biological, Earth, and Environmental Sciences, University of New South Wales, Sydney, Australia; 
  - Liverpool John Moores University, School of Biological and Environmental Sciences, Liverpool, United Kingdom; 
  - European Bioinformatics Institute (EMBL- EBI), European Molecular Biology Laboratory, Wellcome Trust Genome Campus, Hinxton, United Kingdom; 
  - University of Sydney, Charles Perkins Centre, School of Life and Environmental Sciences, School of Mathematics and Statistics, Sydney, Australia; 
  - Division of Ecology and Evolution, Research School of Biology, Australian National University, Canberra, Australia
---

@@

## Introduction
Sex differences arise because selection acts on the two sexes differently, especially on traits associ- ated with mating and reproduction (Darwin, 1871). Therefore, sex differences are widespread, a fact which is unsurprising to any evolutionary biologist. However, scientists in many (bio-)medical fields have not necessarily regarded sex as a biological factor of intrinsic interest (Clayton, 2016; Flanagan, 2014; Karp et al., 2017; Klein et al., 2015; Prendergast et al., 2014; Shansky and Woolley, 2016). Therefore, many (bio-)medical studies have only been conducted with male sub- jects. Consequently, our knowledge is biased. For example, we know far more about drug efficacy in male compared to female subjects, contributing to a poor understanding of how the sexes respond differently to medical interventions (Nowogrodzki, 2017). This gap in knowledge is predicted to lead to overmedication and adverse drug reactions in women (Zucker and Prendergast, 2020). Only recently have (bio-)medical scientists started considering sex differences in their research (Dorris et al., 2015; Ingvorsen et al., 2017; Robinson et al., 2017; Smarr et al., 2017;Ahmad et al., 2017; Foltin and Evans, 2018; Thompson et al., 2018). Indeed, the National Insti- tutes of Health (NIH) have now implemented new guidelines for animal and human research study designs, requiring that sex be included as a biological variable (Clayton, 2016; Clayton and Collins, 2014; NIH, 2015a). 
When comparing the sexes, biologists generally focus on mean differences in trait values, placing little or no emphasis on sex differences in trait variability (see Figure 1 for a diagram explaining differences in means and variances). Despite this, two hypotheses exist that explain why trait variability might be expected to differ between the sexes. Interestingly, these two hypotheses make opposing predictions.

 this stupid figure has to get embedded    
 ![Fig1](./executableMS/Figures/Figure 1.png)

@@

![Fig2](./executableMS/Figures/Figure 2.png)
